---
title: "Cabbages"
author: "Sierra Lander!"
date: "05/21/2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 ###The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following question. 
 
Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$ There is no difference n the average Vitamin  C content of the cabbages based on cultivation method

$H_A$:There is a difference between the average Vitamin C content of  the cabbages based on cultivation methods.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

vitamin C is numerical, Cultivation is categorical

numerical~categorical 
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```
The boxplot shows that cultivation method C52 generally has more vitamin C than C39

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

## Inferential Results
```{r}
t.test(VitC~Cult,data=veggy)
```

P-Value is so small (0.000000034050 ) That we must Reject $H_0$.



<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

Based on results there is a difference between Vitamin C in C39 and C52 cultivation methods. The data shows that the P-value given after doing a T-test is (0.0000000405) this number is LESS than 0.05. This shows that logically there is a difference. 


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
